An Accurate Model for SARS-CoV-2 pooled RT-PCR Test Errors

### 2021-03-31 comment.tex
uri commentz

\begin{abstract}
Pooling is a method of simultaneously testing multiple samples for the presence of pathogens. Pooling of RT-PCR tests of SARS-CoV-2 is increasing in popularity, due to its high testing
throughput. A popular pooling scheme is Dorfman pooling: test $N$
individuals simultaneously. If the test is positive, each individual
is then tested separately; otherwise, all are declared negative. Most analyses of pooling scheme error rates
assume that including more than a single infected sample in a pooled test does not increase the probability of a positive outcome. We challenge this assumption with
experimental data and suggest a novel and parsimonous probabilistic
model for the outcomes of pooled tests. As an application, we analyze
the false-negative rate (i.e., the probability of a negative result
for an infected individual) of Dorfman pooling. We
show that the false-negative rates under Dorfman pooling increase when
the prevalence of infection decreases. However, low infection prevalence is exactly the condition when Dorfman pooling achieves highest throughput efficiency. We therefore implore the cautious use of pooling and developement of pooling strategies that consider the tests' error rates. 
%% This is an inherent problem of Dorfman pooling and should be kept in
%% mind by practitioners and policy makers alike.
\end{abstract}
\newpage

>>>>

\begin{abstract}
Pooling is a method of simultaneously testing multiple samples for the presence of pathogens. Pooling of RT-PCR tests of SARS-CoV-2 is increasing in popularity, due to its high testing
throughput. A popular pooling scheme is Dorfman pooling: test $N$
individuals simultaneously. If the test is positive, each individual
is then tested separately; otherwise, all are declared negative. Most analyses of pooling scheme error rates
assume that including more than a single infected sample in a pooled test does not increase the probability of a positive outcome. We challenge this assumption with
experimental data and suggest a novel and parsimonious probabilistic
model for the outcomes of pooled tests. As an application, we analyze
the false-negative rate (i.e., the probability of a negative result
for an infected individual) of Dorfman pooling. We
show that the false-negative rates under Dorfman pooling increase when
the prevalence of infection decreases. However, low infection prevalence is exactly the condition when Dorfman pooling achieves highest throughput efficiency. We therefore implore the cautious use of pooling and development of pooling strategies that consider the tests' error rates. 
%% This is an inherent problem of Dorfman pooling and should be kept in
%% mind by practitioners and policy makers alike.
\end{abstract}
\newpage
